### 2008-03-21 trunk/Papers/dl-gre-08/discussion.tex
moved figures around

One problem that arises in our approach specifically is that the
bisimulation classes algorithms derive some measure of efficiency from
their freedom to build formulas without having to respect any
linguistic constraints.  It seems straightforward, for instance, to
extend Krahmer et al.'s \shortcite{Krahmer2003} approach such that it
only considers subgraphs that can actually be realized, because their
algorithm proceeds by a genuine search for uniquely identifying
subgraphs, and will simply take a different branch of the search if
some subgraph is useless.  This would be harder in our case.  Our
algorithms don't search in the same way; if we disallow certain
refinements of a partition, we have to allow the algorithms to
backtrack and thus jeopardize the worst-case polynomial runtime.
Investigating this interplay between efficiency and linguistic
constraints is an interesting avenue for future research.

>>>>

One problem that arises in our approach specifically is that both
algorithms derive some measure of efficiency from their freedom to
build formulas without having to respect any linguistic constraints.
It seems straightforward, for instance, to extend Krahmer et al.'s
\shortcite{Krahmer2003} approach such that it only considers subgraphs
that can actually be realized, because their algorithm proceeds by a
genuine search for uniquely identifying subgraphs, and will simply
take a different branch of the search if some subgraph is useless.
This would be harder in our case.  Our algorithms don't search in the
same way; if we disallow certain refinements of a partition, we have
to allow the algorithms to backtrack and thus jeopardize the
worst-case polynomial runtime.  Investigating this interplay between
efficiency and linguistic constraints is an interesting avenue for
future research.
